\ab{Constraints on quasi--normal-mode frequencies with LIGO-Virgo binary--black-hole observations}

### 2021-03-17 papers/intro_paper/discussion.tex
changes in Sec. V

We built a parameterized IMR waveform model that can be used to measure the QNM complex frequencies of the remnant object formed in BBH mergers. This model can be used to analyze any BBH with (aligned-)spinning components, which constitute an important extension of previous work where a similar model for non-spinning components had been considered~\cite{Brito:2018rfr}. We showed that this test can be used to accurately recover the QNM complex frequencies of simulated GW signals in the LIGO and Virgo detectors. We also demonstrated that this model can be used to perform tests of the no-hair conjecture and can also be used to detect possible small deviations from GR in the ringdown part of the signal.

This model had been previously used to analyze BBHs from the first half of LIGO-Virgo's third observing run~\cite{Abbott:2020jks}. We extended these results by analyzing GW events from the first and second LIGO-Virgo observing runs and updated the joint measurements on the fractional deviations in the frequency and damping time of the least-damped QNM. As expected, the event providing the best constraint on the least-damped QNM to be date continues to be GW150914 [see \eqref{GW150914_delta}]. In addition, even in the most agnostic and conservative scenario where we combine the information from different events using an hierarchical approach, at $90\%$ credibility, we constrain the frequency of the least damped QNM to be within $\sim 9\%$ of the GR prediction -- an improvement of a factor of $\sim 4$ over the results reported in~\cite{Abbott:2020jks}. The constraints we obtain on the frequencies and damping time of the least damped QNM are compatible with the ones recently reported in Ref.~\cite{Carullo:2021dui}, where measurements on QNMs were done using only the post-merger part of the signal was analyzed.

>>>>

\ab{We built a parameterized IMR waveform model, $\pSEOB$, that can 
measure the QNM complex frequencies of the remnant object formed \ab{through 
the merger of BHs with aligned or antialigned spins, thus extending  
previous work, which was limited} to non-spinning BHs~\cite{Brito:2018rfr}. 
The $\pSEOB$ model was recently used to infer the QNMs of some of the 
BBH's remnants detected by LIGO and Virgo during O3a~\cite{Abbott:2020jks}.}

We extended these results by analyzing GW events from the first and
second LIGO-Virgo observing runs and updated the joint measurements on
the fractional deviations in the frequency and damping time of the
least-damped QNM. As expected, the event providing the best constraint
on the least-damped QNM to be date continues to be GW150914 [see
\eqref{GW150914_delta}]. In addition, even in the most agnostic and
conservative scenario where we combine the information from different
events using an hierarchical approach, at $90\%$ credibility, we
constrain the frequency of the least damped QNM to be within $\sim
9\%$ of the GR prediction -- an improvement of a factor of $\sim 4$
over the results reported in~\cite{Abbott:2020jks}. The constraints we
obtain on the frequencies and damping time of the least damped QNM are
compatible with the ones recently reported in
Ref.~\cite{Carullo:2021dui}, where measurements on QNMs were done
using only the post-merger part of the signal was analyzed.
